### 2016-08-23 notions.tex
trying to sort out privacy notions, post-crypto chat

\tsnote{Still messing about here, and in the figure.}
In Figure~\ref{fig:privacy-ss} we give a definition capturing semantic-security (of sets)
with respect to the full representation (ss-rep).  In the ``real''
setting (ss-rep-1), a set~$S$ is sampled according to distribution~$\distr{\calS}{}$,
and the adversary is given the~$M,\pubaux$ that result from running
$\Rep(S)$.  It is also provided oracle access to $\QryOracle$.
The adversary must output a function~$f\colon\calS \to \bits^*$ and a
string~$v$ such that $f(S)=v$.  In the ``fake'' setting (ss-rep-0) a
predictor~$P$ is given $\pubaux$ only, and no $\QryOracle$ access.  It
also outputs an $f,v$ pair such that $f(S)=v$.  The advantage of~$A$ (over~$P$)
is $\AdvPrivSS{\Pi,\distr{\calS}{}}{A,P} =
\Prob{\ExpPrivSSreal{\Pi,\distr{\calS}{}}{A}=1} -
\Prob{\ExpPrivSSsim{\Pi,\distr{\calS}{}}{P}=1}$.  To prevent trivial wins
for~$A$, e.g. $f(S)=M$, we forbid~$A$ from outputting~$f$
such that $f(S)=f(S')$ for all $S,S'$ in the support of $\distr{\calS}{}$.

@@

\medskip
\experimentv{$\ExpPrivSSsim{\setprim,\distr{\calS}{}}{P}$}\\
$S\getsr \distr{\calS}{}$\\
$(M,\pubaux,\privaux) \getsr \Rep(S)$\\
$(f,v) \getsr P(\pubaux)$\\
if $f(S)=v$ then\\
\nudge Return 1\\
Return 0\\
}
%
{
\oracle{$\TestOracle(q)$}\\
$a \gets \Qry(M,\pubaux,\privaux,q)$\\
Return~$a$\\
}
}
{
\hpagess{.49}{.49}
{
\experimentv{$\ExpPrivSS{\setprim,\distr{\calS}{},P}{A}$}\\
$S\getsr \distr{\calS}{}$\\
$b \getsr \bits$\\
%$(M,\pubaux,\privaux) \getsr \Rep(S)$\\
$(M_1,\pubaux,\privaux) \getsr \Rep(S)$\\
$M_0 \getsr P(\pubaux)$\\
%$(f,v) \getsr \getsr A^{\TestOracle}(M,\pubaux)$\\
$b' \getsr A^{\TestOracle}(M_b,\pubaux)$\\
%if $f(S)=v$ then\\
if $b'=b$ then\\
\nudge Return 1\\
Return 0\\
%
%\medskip
%\experimentv{$\ExpPrivSSsim{\setprim,\distr{\calS}{}}{P}$}\\
%$S\getsr \distr{\calS}{}$\\
%$(M,\pubaux,\privaux) \getsr \Rep(S)$\\
%$(f,v) \getsr P(\pubaux)$\\
%if $f(S)=v$ then\\
%\nudge Return 1\\
%Return 0\\
}
%
{
\oracle{$\TestOracle(q)$}\\
$a \gets \Qry(M_1,\pubaux,\privaux,q)$\\
Return~$a$\\
}
}
\caption{Semantic-security style privacy definitions. } 
\label{fig:privacy-ss}
\end{figure}
\subsection{Relationships Among Notions}

>>>>

\tsnote{Still messing about here, and in the figure.}
In Figure~\ref{fig:privacy-ss} we give a definition capturing semantic-security (of sets)
with respect to the full representation (ss-rep).  In the ``real''
setting (ss-rep-1), a set~$S$ is sampled according to distribution~$\distr{\calS}{}$,
and the adversary is given the~$M,\pubaux$ that result from running
$\Rep(S)$.  It is also provided oracle access to $\TestOracle$.
The adversary must output a function~$f\colon\calS \to \bits^*$ and a
string~$v$ such that $f(S)=v$.  In the ``fake'' setting (ss-rep-0) a
predictor~$P$ is given $\pubaux$ only, and no $\TestOracle$ access.  It
also outputs an $f,v$ pair such that $f(S)=v$.  The advantage of~$A$ (over~$P$)
is $\AdvPrivSS{\Pi,\distr{\calS}{}}{A,P} =
\Prob{\ExpPrivSSreal{\Pi,\distr{\calS}{}}{A}=1} -
\Prob{\ExpPrivSSsim{\Pi,\distr{\calS}{}}{P}=1}$.  To prevent trivial wins
for~$A$, e.g. $f(S)=M$, we forbid~$A$ from outputting~$f$
such that $f(S)=f(S')$ for all $S,S'$ in the support of $\distr{\calS}{}$.

@@

\medskip
\experimentv{$\ExpPrivSSsim{\setprim,\distr{\calS}{}}{P}$}\\
$S\getsr \distr{\calS}{}$\\
$(M,\pubaux,\privaux) \getsr \Rep(S)$\\
$(f,v) \getsr P(\pubaux)$\\
if $f(S)=v$ then\\
\nudge Return 1\\
Return 0\\
}
%
{
\oracle{$\TestOracle(q)$}\\
$a \gets \Qry(M,\pubaux,\privaux,q)$\\
Return~$a$\\
}
}
{
\hpagess{.49}{.49}
{
\experimentv{$\ExpPrivSS{\setprim,\distr{\calS}{},P}{A}$}\\
$S\getsr \distr{\calS}{}$\\
$b \getsr \bits$\\
%$(M,\pubaux,\privaux) \getsr \Rep(S)$\\
$(M_1,\pubaux,\privaux) \getsr \Rep(S)$\\
$M_0 \getsr P(\pubaux)$\\
%$(f,v) \getsr \getsr A^{\TestOracle}(M,\pubaux)$\\
$b' \getsr A^{\TestOracle}(M_b,\pubaux)$\\
%if $f(S)=v$ then\\
if $b'=b$ then\\
\nudge Return 1\\
Return 0\\
%
%\medskip
%\experimentv{$\ExpPrivSSsim{\setprim,\distr{\calS}{}}{P}$}\\
%$S\getsr \distr{\calS}{}$\\
%$(M,\pubaux,\privaux) \getsr \Rep(S)$\\
%$(f,v) \getsr P(\pubaux)$\\
%if $f(S)=v$ then\\
%\nudge Return 1\\
%Return 0\\
}
%
{
\oracle{$\TestOracle(q)$}\\
$a \gets \Qry(M_1,\pubaux,\privaux,q)$\\
Return~$a$\\
}
}
\caption{Semantic-security style privacy
  definitions. \textcolor{red}{On the left, need to protect against
    adversary outputting
    things like $f(S)=M$.  One idea is to forbid~$f$ such that
    $f(S)=f(S')$ for all $S,S'$ in the support of $\distr{\calS}{}$.}
    } 
\label{fig:privacy-ss}
\end{figure}
\subsection{Relationships Among Notions}
